### 2018-01-19 Paper/jaccardbaetica.tex
material and method update

\journal{Journal of Archaeological Science}

\bibliographystyle{model2-names.bst}\biboptions{authoryear}

@@

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The meaning of stamp is still under debate. Some authors suggest that they were identified as the owner of the olive land \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owner of the amphorae workshop. In any case, the use of these stamps defined the system of working in the workshops.

The information of the stamps is known as tria nomina (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE)and contend

%habría que citar a Dressel

@@

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the similarity between sets. In our case, Jaccard distance was used to calculate the mutual presence of traits in the stamps.

%should i include morisita o horn

\subsection{Dissimilarity}

This method is used to measure the overlap between different samples of sets. 
%hablar sobre Horn (Morisita)

>>>>

%\journal{Journal of Archaeological Science}

%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

@@

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The information of the stamps is known as \textit{tria nomina} (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE). \textit{Tria Nomina} was mostly formed for a code of three letters.

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the owner of the olive land \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owner of the amphorae workshop. In any case, the use of these stamps defined the system of working in the workshops. 
%habría que citar a Dressel

@@

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity between sets. In our case, Jaccard distance was used to calculate the mutual presence of traits in the stamps. A comparison was done with the distance of the workshops to know whether there was an association between stamps and spatial distance.

\subsection{Dissimilarity correlation}

This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. Unlike Jaccard distance, Morisita-Horn variant can be used to handle large samples with different sizes and diversity. The index can be described  where 0 is no presence of overlap and 1 totally similarity. 
%hablar sobre Horn (Morisita)
